On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-12-16 techreport.tex
Add 6 figures.

\section{Evaluations}
\label{sec:sim}
We have rigorously shown that our incentive mechanism can resist any collusion attacks, even with profit trading. In this section, we use experimental results to evaluate the performance of our mechanism. We consider the following aspects when evaluating: 
\begin{itemize}
\item \emph{Running time}, which is the average responding time to answer one user's application. After receiving any user $i$'s strategy $s_i$, we expect the platform will give the response $(n_i,p_i)$ as soon as possible.
\item \emph{Utilization of the budget}, which is the ratio between the payment sum and the budget $B$. Let $\rho$ be the utilization ratio. Then we have
\begin{equation}
\label{eqn:ur}
\rho = \frac{\sum_{i\in U}p_i}{B}.
\end{equation}
\item \emph{Completion of the sensing tasks}, which is the ratio between the number of finished tasks and the total sum of all the tasks. This ratio should be positively related to the budget $B$ as incentives.
\end{itemize}

\subsection{Experiment Setup}
We implemented our mechanism and the algorithm in \cite{koutsopoulos2013optimal} using Python 2.7. We ran the programs on 4-core Intel Xeon Processors with 16GB RAM, and SMP Linux with kernel version 3.19.8.

@@

>>>>

\section{Evaluations}
\label{sec:sim}
We have rigorously shown that our incentive mechanism can resist any collusion attacks, even with profit trading. In this section, we use experimental results to evaluate the performance of our mechanism. We consider the following aspects when evaluating: 
\begin{itemize}
\item \emph{Running time}, which is the average responding time to answer one user's application. After receiving any user $i$'s strategy $s_i$, we expect the platform will give the response $(n_i,p_i)$ as soon as possible.
\item \emph{Utilization of the budget}, which is the ratio between the payment sum and the budget $B$. Let $\rho$ be the utilization ratio. Then we have
\begin{equation}
\label{eqn:ur}
\rho = \frac{\sum_{i\in U}p_i}{B}.
\end{equation}
\item \emph{Completion of the sensing tasks}, which is the ratio between the number of finished tasks and the total sum of all the tasks. This ratio should be positively related to the budget $B$ as incentives.
\end{itemize}
For each item we consider two variables: the number of participating users and the budget.

\subsection{Experiment Setup}
We implemented our mechanism and the algorithm in \cite{koutsopoulos2013optimal} using Python 2.7. We ran the programs on 4-core Intel Xeon Processors with 16GB RAM, and SMP Linux with kernel version 3.19.8. Each measurement takes 1000 test samples.

@@

\begin{figure*}[!t]
\centering
\begin{minipage}{0.31\textwidth}
\includegraphics[width=\textwidth]{collusion_resist_codes/images/img_running_time.eps}
\caption{Running time with different sizes of participating users.}
\label{fig:running_time_n}
\end{minipage}
\hspace{0.01cm}
\begin{minipage}{0.31\textwidth}
\includegraphics[width=\textwidth]{collusion_resist_codes/images/img_running_time_R.eps}
\caption{Running time with different budgets.}
\label{fig:running_time_R}
\end{minipage}
\hspace{0.01cm}
\begin{minipage}{0.31\textwidth}
\includegraphics[width=\textwidth]{collusion_resist_codes/images/img_rho.eps}
\caption{Budget utilization ratio with different sizes of users.}
\label{fig:rho_n}
\end{minipage}
\end{figure*}

\begin{figure*}[!t]
\centering
\begin{minipage}{0.31\textwidth}
\includegraphics[width=\textwidth]{collusion_resist_codes/images/img_rho_R.eps}
\caption{Budget utilization ratio with different budgets.}
\label{fig:rho_R}
\end{minipage}
\hspace{0.01cm}
\begin{minipage}{0.31\textwidth}
\includegraphics[width=\textwidth]{collusion_resist_codes/images/img_rtask_n.eps}
\caption{Finished task ratio with different sizes of users.}
\label{fig:rtask_n}
\end{minipage}
\hspace{0.01cm}
\begin{minipage}{0.31\textwidth}
\includegraphics[width=\textwidth]{collusion_resist_codes/images/img_rtask.eps}
\caption{Finished task ratio with different budgets.}
\label{fig:rtask_R}
\end{minipage}
\end{figure*}
